Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-10-18 manu-draft.Rmd
gam seasonal estimate plot added

>>>>

```{r wqgamtrnds, fig.cap = 'Predicted (a) total nitrogen (mg/L), (b) chlorophyll-a (ug/L), and (c) secchi disk depth (meters) by area based on historal seasonal models.  Estimated trends are based on Generalized Additve Models fit to historical basline data from 2006 to early 2021.  Predicted trends from the historical models for dates during and after the Piney Point discharge are shown in thick lines (+/- 95% confidence), with observed samples overlaid on the plots.  Results are grouped by assessment areas shown in Figure \\@ref(fig:map)a.'}
knitr::include_graphics(here('figs/wqgamtrnds.jpeg'))
```
